Mechanising Hylomorphisms for Extraction of Executable Code

### 2025-03-18 paper/lensbans.tex
banana
lenses

@@

\newsavebox{\llensbox}
\newcommand{\llensmacro}{%
\begin{tikzpicture}[baseline=0.45ex,xscale=0.006em,yscale=0.012ex]%
\draw[solid,join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9) to[out=-120, in=90] (0.7,3) to[out=-90, in=120] (1.5,0.1) -- cycle;%
\end{tikzpicture}}
\savebox{\llensbox}{\llensmacro}
\newcommand{\llens}{\mathopen{\usebox{\llensbox}\mspace{1mu}}}

\newsavebox{\rlensbox}
\newcommand{\rlensmacro}{%
\begin{tikzpicture}[baseline=0.45ex,xscale=-0.006em,yscale=0.012ex]%
\draw[solid,join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9) to[out=-120, in=90] (0.7,3) to[out=-90, in=120] (1.5,0.1) -- cycle;%
\end{tikzpicture}}
\savebox{\rlensbox}{\rlensmacro}
\newcommand{\rlens}{\mathclose{\mspace{1mu}\usebox{\rlensbox}}}

>>>>

\newsavebox{\lbananabox}
\newcommand{\lbananamacro}{%
  \begin{tikzpicture}[baseline=0.25em,xscale=0.005em,yscale=0.005em]
  \draw[solid, join=round] (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;
\end{tikzpicture}
}
\savebox{\lbananabox}{\lbananamacro}
\newcommand{\lbanana}{\mathopen{\usebox{\lbananabox}\hspace{-0.6ex}}}

\newsavebox{\rbananabox}
\newcommand{\rbananamacro}{%
  \begin{tikzpicture}[baseline=0.25em,xscale=-0.005em,yscale=0.005em]
  \draw[solid, join=round] (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;
  \end{tikzpicture}
}
\savebox{\rbananabox}{\rbananamacro}
\newcommand{\rbanana}{\mathclose{\usebox{\rbananabox}}}

@@

\newsavebox{\llensbox}
\newcommand{\llensmacro}{%
\begin{tikzpicture}[baseline=0.25em,xscale=0.006em,yscale=0.006em]
\draw[solid, join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9) to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;%
\end{tikzpicture}}
\savebox{\llensbox}{\llensmacro}
\newcommand{\llens}{\mathopen{\usebox{\llensbox}\mspace{1mu}}}

\newsavebox{\rlensbox}
\newcommand{\rlensmacro}{%
\begin{tikzpicture}[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
  \draw[join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
  to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;
\end{tikzpicture}}
\savebox{\rlensbox}{\rlensmacro}
\newcommand{\rlens}{\mathclose{\mspace{1mu}\usebox{\rlensbox}}}
